ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-08 paper/paper.tex
update

For a N-folds stacking:

@@

 \item Predict $testing$ and $training_1$ using original features from $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) with first stage models

 \item Similarly for $training_2, training_3, ... training_N$, the prediction for testing is the average of $N$ predictions of $testing$

 \item Train the second stage model based on original features and first stage predictions
\end{enumerate}
%

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=100mm]{Rplot.png}
\caption{Task 2 $AUC$ of 5-folds CV result (Same parameters) and Prediction on 30\% testing data using different number of stacking features.
 The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}

>>>>

For a N-folds stacking using single first stage model:

@@

 \item Build stacking feature by predicting $testing$ and $training_1$ using original features from $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) with first stage model

 \item Similarly for $training_2, training_3, ... training_N$, the stacking feature for $testing$ is the average of $N$ predictions of $testing$

 \item Train the second stage model based on original features and stacking feature
\end{enumerate}
%

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=95mm]{Rplot.png}
\caption{Task 2 $AUC$ of 5-folds CV result (Same parameters) and Prediction on 30\% testing data using different number of stacking features.
 The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}
